\thesistitle

### 2019-07-04 sections/research.tex
Formatting
Type 2 shortcomings

\subsection{Type 2 clones}\label{sec:type2}
  Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments} \cite{roy2007survey}. This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified. The two methods displayed in figure \ref{fig:type2} are type 2 clones of each other.

@@

Looking at the example in figure \ref{fig:type2}, we see an example of a type 2 clone that poses no harm to the design of the system. Both methods are, except for their matching structure, completely different in functionality. They operate on different types, call different methods, return different things, etc. Having such a method flagged as a clone does not provide much useful information.

When looking at refactoring, type 2 clones can be very difficult to refactor. For instance if we have variability in types, the code can describe operations on two completely dissimilar types. Type 2 clones do not differentiate between primitives and objects, which makes the these clones often not so useful for refactoring purposes.

>>>>

\subsection{Type 2 clones}\label{sec:type2}
Type 2 clones are \textit{structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments}~\cite{roy2007survey}. This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified. However, the definition does not adequately differentiate between slight modification and completely different fragments that just happen to have the same structure.

For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore. This could render two methods that have an entirely different functionality as clones. Merging such clones can be harmful instead of helpful.

@@

The example in Fig.~\ref{fig:type2} shows a type 2 clone that poses no harm to the design of the system. Both methods are, except for their matching structure, completely different in functionality. They operate on different types, call different methods, return different things, etc. Having such a method flagged as a clone does not provide much useful information.

When looking at refactoring, type 2 clones can be difficult to refactor. For instance, if we have variability in types, the code can describe operations on two completely dissimilar types. Type 2 clones do not differentiate between primitives and reference types, which further undermines the usefulness of clones detected by this definition.
